\newcommand{\studentName}{%
\vspace{0.5em}\small student: \rule{50mm}{.1pt}
}


\title{CS418 Milestone 1 Grade Sheet \\\studentName}
\date{\vspace{-10ex}}

\documentclass[12pt]{article}
\usepackage[margin=2cm]{geometry}
\begin{document}
\maketitle

\newcommand{\grade}[1]{\item[\rule{5mm}{.1pt}/#1]}


\let\oldenumerate\itemize
\renewcommand{\itemize}{
  \oldenumerate
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}

{\footnotesize
\section*{\normalsize Base Requirements}
\begin{itemize}
\grade{2} The web site must provide a web page that allows a registered user to submit a question to the website. This user is the ASKER in the below requirements.
\grade{1} Users must be able to log into your web site using the credentials supplied. There is no need to implement new user registration.
\grade{1} The user login process must use the HTTP POST method.
\grade{1} Questions shall be stored in a MySQL database with a reference to the ASKER. Answers corresponding to questions shall be stored in the database as well.
\grade{1} The question submission interface must minimally consist of a ``title'' text field and a ``content'' text field and use HTML forms.
\grade{1} For each question, allow other registered users to submit answers to the questions (potentially multiple answers per user per question).
\grade{1} Other answers to a question must be displayed along with the associated question.
\grade{2} The ASKER shall have the ability to mark the answer they feel answers their question best. See StackOverflow's checkmark on answers as an example of this.
\grade{2} The question display interface must minimally consist of the question contents, associated answers, the author of the question/answers, and an indicator of the answer marked by the ASKER.
\grade{2} The home page for your web site must provide links to the questions previously asked, minimally including the question title.
\grade{1} No corrections needed to codebase come demo day.
\end{itemize}

\section*{\normalsize Brief Project Writeup}
\begin{itemize}
\grade{3} Submitted on demo day - How is each requirement met, design decisions, programming tricks, helpful resources consulted
\end{itemize}

\section*{\normalsize Website Usability}
\begin{itemize}
\grade{3} How easy is the site to use
\end{itemize}

\section*{\normalsize Website Aesthetics}
\begin{itemize}
\grade{2} How nice does the site look
\end{itemize}

\section*{\normalsize Midway Status Report}
\begin{itemize}
\grade{2} 3-4 min presentation on assignment progress
\end{itemize}

{\centering 
\framebox[1.0\linewidth]{\Large MILESTONE 1 GRADE: \rule{10mm}{.1pt}/25}
}

\pagenumbering{gobble}
\end{document}